\section{Frequently Asked Questions}
\label{sec:faq}

\textbf{Note:} %
This FAQ section may be removed in later versions of this manual. %
There is always an up-to-date FAQ list on Github (\cite{web-scam}). %

\begin{itemize}
\item \textbf{The property generation takes a very long time/doesn't
    finish:} Please try to split up your design into several
  sections. %
  This helps the tool during property generation. %
  It is best to put each communication call into a separate section. %

\item \textbf{else with only one undetected statement $\rightarrow$
    CFG error}: This is usually due to a case that should never
  occur. %
  \DSWON{%
?!? If it happens ``usually'', how can it ``never occur''?%
}%
People throw an exception or write an assertion for this case. %
  Obviously this doesn't translate to hardware. %
  \DSSAY{%
This is really cryptic...%
}%


\item \textbf{Multiple path possible from init:} Usually after state merging
  the reset sequence depends on an input value. %

\item \textbf{Properties with compound/enum types:} If your design
  uses compound/enum types they will also be used within the
  properties. %
  The user has two options: either define the types themselves or run
  \SCAM{} with -VHDL and extract the package defining all user-defined
  types. %

\item Don't use reserverd VHDL keywords as names for variables, in
  enum types or anything else. %

\item overflow arithmetic use (31 downto 0) in the properties. %

\DSWON{%
Where are the questions/answers to the last two items? %
}%


\end{itemize}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "binder"
%%% End: 
